Toward a Comparable Corpora of Latvian, Russian and English Tweets

### 2017-04-18 paper.tex
Minor

The initial set of tweets was retrieved by subscribing to the \texttt{POST status/filter} endpoint of the Twitter Streaming API\footnote{\url{https://dev.twitter.com/streaming/reference/post/statuses/filter}}.
%with Poultry \cite{dmitrijs_milajevs_2017_546609}
The collected tweets had to be geo-located and had to originate from the area of Riga, the capital of Latvia.\footnotemark{}

@@

Further analysis of the extended rehydrated collection showed that there are 23\,115 (10.5\%) tweets that originated from check-ins with on Foursquare.\footnote{\url{https://foursquare.com}} This motivated additional filtering of the rehydrated collection, as ``check-in tweets'' most of the time follow a predefined template and thus do not reflect real language use. # What does this mean and why?

@@

\section{Timeline analysis}
\label{sec:timeline}

@@

Figure~\ref{fig:timeline} shows the bandwidth of tweets over time for all three languages. There are several peaks in Twitter usage. Some of them affect all three languages, as in early January, some of them affect only one language, as in late January. # Any significance? Ah, I see next paragraph.

@@

\section{Language use}
\label{sec:lang-use}

>>>>

The initial set of tweets was retrieved by subscribing to the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnote{\url{https://dev.twitter.com/streaming/reference/post/statuses/filter}}
%with Poultry \cite{dmitrijs_milajevs_2017_546609}
The collected tweets had to be geo-located and had to originate from the area of Riga, the capital of Latvia.\footnotemark{}

@@

Further analysis of the extended rehydrated collection showed that there are 23\,115 (10.5\%) tweets that originated from check-ins with on Foursquare.\footnote{\url{https://foursquare.com}} This motivated additional filtering of the rehydrated collection, as ``check-in tweets'' most of the time follow a predefined template and thus do not reflect real language use. % What does this mean and why?

@@

\section{Tweet analysis}
\label{sec:timeline}

@@

Figure~\ref{fig:timeline} shows the bandwidth of tweets over time for all three languages. There are several peaks in Twitter usage. Some of them affect all three languages, as in early January, some of them affect only one language, as in late January. % Any significance? Ah, I see next paragraph.

@@

\section{User analysis}
\label{sec:lang-use}
